%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Add various styling and section options and allow for multiple pages smoothly.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.3:
% 1. Removed MacFonts version as I have no desire to maintain it nor access to macOS
% 2. Switched column ordering
% 3. Changed font styles/colors for easier human readability
% 4. Added, removed, and rearranged sections to reflect my own experience
% 5. Hid last updated
%
% v1.2:
% 1. Added publications in place of societies.
% 2. Collapsed a portion of education.
% 3. Fixed a bug with alignment of overflowing long last updated dates on the top right.
%
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jesus Daniel Gonzalez Rocha}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:john.doe@example.com}{daniel.gonzalez13@uabc.edu.mx} | \href{tel:+1111111111111}{+52.664.766.9864}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Profile}
Passionate about software development, with a strong focus on C and Python programming languages. Enthusiastic about leveraging my skills to solve complex problems, particularly in the field of Artificial Intelligence (AI). 
With hands-on experience in developing AI models and algorithms, I aim to contribute to cutting-edge projects that push the boundaries of technology. Constantly exploring new trends and techniques in AI to stay at the forefront of innovation, I thrive in collaborative environments where I can apply my problem-solving abilities and coding expertise.
\sectionsep

\section{Experience}
\runsubsection{Faculty of Dentistry}
\descript{| Assistant Technical Support}
\location{Jan 2024 – Jul 2024 | Tijuana, Mexico}
\vspace{1em}
\begin{tightemize}
\item Provided technical support in the Faculty of Dentistry, with a focus on server maintenance and resolving issues with machines.
\item Performed routine server maintenance to ensure optimal performance and minimize downtime for faculty operations.
\item Diagnosed and resolved technical issues related to specialized dental equipment, ensuring minimal disruption to clinical and academic activities.
\item Collaborated with faculty staff to address urgent IT needs, providing effective solutions to enhance workflow and operational efficiency.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Neural Network Library Development}
\descript{Team leader| Class Project for Neural Network}
\location{Aug 2023 – Dec 2023 | Tijuana, Mexico}
\begin{tightemize}
\item Led the development of a custom \textbf{\href{https://github.com/Dan1543/Neural-Network}{neural network library}} neural network library, coordinating a team of developers to build functionalities for deep learning models.
\item Implemented core modules for layer definitions, back-propagation, and optimization algorithms, primarily in Python.
\item Focused on creating an efficient, modular, and extensible architecture to facilitate various neural network configurations.
\item Conducted regular code reviews, mentored team members, and ensured adherence to project timelines.
\end{tightemize}
\sectionsep

\runsubsection{Tracking Roles of Alumni in Computer Engineering}
\descript{| Front-End Leader | Class Project for Software Engineering}
\location{Feb 2023 – Jul 2023 | Tijuana, Mexico}
\begin{tightemize}
\item Led the front-end development of the \textbf{\href{https://github.com/Proyecto-TRACE}{Trace Project}} for tracking and visualizing the career paths of Computer Engineering alumni.
\item Integrated a map API to display real-time geographic locations of alumni, enabling dynamic updates and interaction on the map.
\item Developed responsive UI components using HTML, CSS, and JavaScript to create a user-friendly experience across devices.
\item Collaborated closely with back-end developers to ensure smooth API data integration and efficient data flow.
\item Focused on enhancing user engagement by implementing interactive features for exploring alumni career paths and locations.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
% \location{Jan 2014 – Jan 2015 | Ithaca, NY}
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.
% \sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COMMUNITY SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Community Service}

% \begin{tabular}{rll}
% 2013 -- 2018    & Tennessee     & St. Baldrick's Foundation\\
% 2014 -- 2017	& Tennessee     & American Cancer Society's Hope Lodge\\
% 2013 -- 2015    & Tennessee     & Habitat for Humanity\\
% 2011 -- 2015    & Tennessee     & Special Olympics\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies}

% \begin{tabular}{rll}
% 2018 -- 2018    & National      & Association of Computing Machinery (ACM)\\
% 2017 -- 2019	& National      & Scrum Alliance Certified ScrumMaster\\
% 2015 -- 2019    & University    & Shackouls Honors College\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards}
% \begin{tabular}{rll}
% 2015        & 99\textsuperscript{th} percentile & National Merit Scholarship Finalist\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications}
% \renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Universidad Autonomoma de Baja California}
\descript{Bachelor of Science in Computer Science}
\location{Aug 2020 | Actual}
% College of Engineering \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{3+ years:}
Python \textbullet{} C \\
\location{1+ years:}
Matlab \\
\location{0+ years:}
JavaScript \textbullet{} Java \\
\sectionsep

\subsection{Technology}
Git/Github \textbullet{} Linux \\
UNIX \textbullet{} Windows \textbullet{} Embedded Systems \\
Artificial Intelligence \textbullet{} Automation \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Quantum Computing}
\descript{| Researcher}
\location{Jan 2023 – Jul 2023 | Tijuana, Mexico}
Conducted research in quantum computing as part of a collaborative team under the supervision of Prof. J. Reyes Juarez Ramirez.
Collaborated with teammates \textbf{\href{https://www.linkedin.com/in/andres-barrera-34a488281/}{Andres Barrera}} and \textbf{\href{https://www.linkedin.com/in/ian-pescador-robles-03360128a/}{Ian Pescador}} to develop algorithms focused on quantum computing applications.
Focused on applying quantum algorithms to optimize specific computational problems, conducting experiments and analyzing outcomes.
Contributed to the development of technical documentation and presented findings in faculty seminars.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/Dan1543}{\bf Dan1543} \\
LinkedIn://  \href{https://www.linkedin.com/in/jesus-daniel-gonzalez-rocha-93010b28b/}{\bf Jesus Daniel Gonzalez Rocha}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
